Keyword and Collocation analysis on India-related text of Natural History

### 2023-06-28 paper_quarto.qmd

[^2]: Given the challenges in precisely determining the coordinate range during the 1st century BC, the coordinate range of modern India is applied as a rough approximation.

@@

In conclusion, the keywords extracted from the India-related text in the *Natural History* shed light on India's role in trade, the production of valuable goods, and its association with notable historical figures and geographical features within the perspective of Pliny the Elder during the 1st century BC in the context of the Roman Empire. These findings could also contribute to a better understanding of India's historical interactions with the broader ancient world.

@@

Within the context of Pliny the Elder's *Natural History* is a book with an encyclopedia scope written in Roman Empire, these collocates suggest the interconnecting role India played in the network of interactions, trade, or cultural exchanges between India and the Mediterranean regions during 1st century BC. They highlight India's significance as a trading partner, its geographical positioning, and the recognition of its territorial boundaries.

@@

The analysis of keywords in the India-related text revealed significant themes such as the rivers, gemstones, goods, and historical figures like Megasthenes. These findings emphasize the cultural, geographical, and historical importance of India in the scope of scholars in Roman Empire during 1st century BC.

>>>>

[^2]: Given the challenges in precisely determining the coordinate range during the 1st century AD, the coordinate range of modern India is applied as a rough approximation.

@@

In conclusion, the keywords extracted from the India-related text in the *Natural History* shed light on India's role in trade, the production of valuable goods, and its association with notable historical figures and geographical features within the perspective of Pliny the Elder during the 1st century AD in the context of the Roman Empire. These findings could also contribute to a better understanding of India's historical interactions with the broader ancient world.

@@

Within the context of Pliny the Elder's *Natural History* is a book with an encyclopedia scope written in Roman Empire, these collocates suggest the interconnecting role India played in the network of interactions, trade, or cultural exchanges between India and the Mediterranean regions during 1st century AD. They highlight India's significance as a trading partner, its geographical positioning, and the recognition of its territorial boundaries.

@@

The analysis of keywords in the India-related text revealed significant themes such as the rivers, gemstones, goods, and historical figures like Megasthenes. These findings emphasize the cultural, geographical, and historical importance of India in the scope of scholars in Roman Empire during 1st century AD.
